Pillar 1 - Student Topic Profile

### 2019-04-16 Pillar 1 - Topic Profile.Rmd

```{r student_GPA, cache = T}
student_GPA <- d_transcript_augmented %>%

@@

# Join student TP and GPA
```{r student_profile}
d_transcript_augmented <- d_transcript_augmented %>%

@@

  left_join(student_TP , by = c("Student ID", "time")) %>%

@@

  # Results from CV
  mutate(m_lasso      = cv %>% map    (~ .[["glmnet.fit"]]),
         lambda_min   = cv %>% map_dbl(~.[["lambda.min"]]),
         lambda_1se   = cv %>% map_dbl(~.[["lambda.1se"]]),
         index_best   = cv %>% map_dbl(~ which.min(.[["cvm"]])),
         cv_error     = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]),
         cv_error_sd  = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvsd"]][..2])
         ) %>%

@@

## find alpha

@@

d_transcript_augmented_app <- d_transcript_augmented %>%

@@

save(fit_lasso_app, d_transcript_augmented_app, d_prep, file = "APP/Recommender System/grade_prediction.RDATA")
```

@@

student_profile <- d_transcript_augmented_app %>%

@@

  mutate(prediction = cv %>% map_dbl(my_predict, student_profile)) %>%

@@

>>>>

```{r student_GPA, cache = TRUE}
student_GPA <- d_transcript_augmented %>%

@@

# Join student TP and GPA
```{r student_profile, cache = TRUE}
student_profile <- d_transcript_augmented %>%

@@

  left_join(student_TP , by = c("Student ID", "time"))
```

```{r}
student_profile_nest <- student_profile %>%

@@

  # Results from CV
  mutate(m_lasso      = cv %>% map    (~ .[["glmnet.fit"]]),
         lambda_min   = cv %>% map_dbl(~ .[["lambda.min"]]),
         lambda_1se   = cv %>% map_dbl(~ .[["lambda.1se"]]),
         index_best   = cv %>% map_dbl(~ which.min(.[["cvm"]])),
         cv_error     = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]),
         cv_error_sd  = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvsd"]][..2])
         ) %>%

@@

@@

student_profile_nest_app <- student_profile_nest %>%

@@

save(fit_lasso_app, student_profile_nest_app, d_prep, file = "APP/Recommender System/grade_prediction.RDATA")
```

@@

student_prof <- student_profile_nest_app %>%

@@

  mutate(prediction = cv %>% map_dbl(my_predict, student_prof)) %>%

@@

# Extra: find best alpha

Best alpha turns out to be 1 (lasso). Good, because predictor regularization also serves as predictor selection.
